Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

@@

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-amaxb,-0.1, 0, 0.1, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-1.05*amaxb, 1.05*amaxb),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(0,0,0,0,"pt"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

    plot.gtable.alpha.diversity.stripped <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
    return(list(plot = plot.gtable.alpha.diversity.stripped$grobs[[6]],
                yaxis = plot.alpha.diversity.yaxis,
                xaxis = plot.alpha.diversity.gtable$grobs[[7]],
                legend = plot.alpha.diversity.legend))
}

@@

g4 <- arrangeGrob(grobs = gs4,
            layout_matrix = rbind(
                c(1,    2,    3, 4),
                c(NA, 5,    6, NA),
                c(NA, NA, 7, NA)),
            widths=c(4, 0.7, 5, 5),
            heights=c(10, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)
```

>>>>

adonis.species$min

@@

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-amaxb,-0.1, 0, 0.1, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-1.05*amaxb, 1.05*amaxb),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(t = 1, unit = "cm"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

    plot.gtable.alpha.diversity.stripped <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
    return(list(plot = plot.gtable.alpha.diversity.stripped$grobs[[6]],
                yaxis = plot.alpha.diversity.yaxis,
                xaxis = plot.alpha.diversity.gtable$grobs[[7]],
                legend = plot.alpha.diversity.legend))
}
```

@@

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(1,    2,    3, NA, NA),
                      c(1,    2,    3, NA, 4),
                      c(NA, 5,    6, NA, NA),
                      c(NA, NA, 7, NA, NA)),
                  widths=c(4, 0.7, 5, 0.7, 3),
            heights=c(3, 7, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

### 2019-01-25 rrbiome.Rmd
Minor

 ```{r adonis calculation, cache = FALSE}
if (!file.exists("rds/adonis.species.rds")) {

    adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                        covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                    npermutations = 1)

    saveRDS(adonis.species, file = "rds/adonis.species.rds")

} else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

>>>>

 ```{r adonis calculation, cache = FALSE}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 99)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 99)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
